I/O simulation model with Linux page cache, integration and evaluation in SimGrid framework

### 2020-06-04 paper_io_sim.tex
Minor fix

			\begin{algorithm}\caption{Read}\label{alg:read}
				\small
				\begin{algorithmic}[1]
					\Input
        				\Desc{fn}{file name}
        				\Desc{fs}{file size}
						\Desc{rt}{current simulated run time}
						\Desc{mm}{MemoryManager object}
						\Desc{$r_m$}{memory read bandwidth}
						\Desc{$r_d$}{disk read bandwidth}
   					\EndInput
   					\Output
						\Desc{rt}{simulated run time after the file is read}
   					\EndOutput
					\State mem\_required = max(0, 2*fs - mm.cached\_data(fn) - 
					mm.available\_memory()) 
					\State mem\_avail = max(0, 2 * fs - mm.cached\_data(fn) - 
					mm.dirty\_data())
					\State rt = rt +  mm.flush(mem\_required - 
					mem\_avail)	
					\State free\_mem\_required = max(0, 2 * fs - mm.cached\_data(fn) - 
					mm.free\_memory())
					\State mm.evict(free\_mem\_required) 
					\If {mm.cached\_data(fn) $>$ 0}
    					\State mm.cache\_read(fn) 
						\If {mm.cached\_data(fn) == fs}
    						\State time = mm.cache\_data(fn) / $r_m$
    						\State IOController.periodic\_flush(time) 
							\State rt = rt + time
						\EndIf
					\EndIf
					\If {mm.cached\_data(fn) $<$ fs}
						\State rt = rt + IOController.flush(mm.dirty\_data())
						\State mm.disk\_read(fs - mm.cache\_data(fn), fn)
    					\State rt = rt + (fs - mm.cache\_data(fn)) / $r_d$
					\EndIf

@@

			Data flushing is another key function in our simulator. It takes 
			the input as the amount of flushed data and the returned value is the 
			simulated flushing time. To flush dirty data, IOController simply 
			traverses the sorted inactive and active list, reduces the dirty data 
			amount by unmarking dirty blocks until the flushed amount reached 
			the amount passed in or there is no dirty data left in cache. 
			Similarly, periodical flushing is the function that simulates data flushing 
			during CPU time and cache read. However, the flushed data amount is 
			calculated with the input which is flushing time. In both flushing 
			functions, the last block being flushed is split if its data is not 
			entirely flushed.

>>>>

			\begin{algorithm}\caption{Read}\label{alg:read}
				\small
				\begin{algorithmic}[1]
					\Input
        				\Desc{fn}{file name}
        				\Desc{fs}{file size}
						\Desc{rt}{current simulated run time}
						\Desc{mm}{MemoryManager object}
						\Desc{$r_m$}{memory read bandwidth}
						\Desc{$r_d$}{disk read bandwidth}
   					\EndInput
   					\Output
						\Desc{rt}{simulated run time after the file is read}
   					\EndOutput
					\State mem\_required = max(0, 2 * fs - mm.cached\_data(fn) - 
					mm.available\_memory()) 
					\State mem\_avail = max(0, 2 * fs - mm.cached\_data(fn) - 
					mm.dirty\_data())
					\State rt = rt +  mm.flush(mem\_required - 
					mem\_avail)	
					\State free\_mem\_required = max(0, 2 * fs - mm.cached\_data(fn) - 
					mm.free\_memory())
					\State mm.evict(free\_mem\_required) 
					\If {mm.cached\_data(fn) $>$ 0}
    					\State mm.cache\_read(fn) 
						\If {mm.cached\_data(fn) == fs}
    						\State time = mm.cache\_data(fn) / $r_m$
    						\State IOController.periodic\_flush(time) 
							\State rt = rt + time
						\EndIf
					\EndIf
					\If {mm.cached\_data(fn) $<$ fs}
						\State rt = rt + IOController.flush(mm.dirty\_data())
						\State mm.disk\_read(fs - mm.cache\_data(fn), fn)
    					\State rt = rt + (fs - mm.cache\_data(fn)) / $r_d$
					\EndIf

@@

			Data flushing is another key function in our simulator. It takes 
			the input as the amount of flushed data and the returned value is the 
			simulated flushing time. To flush dirty data, IOController simply 
			traverses the sorted inactive and active list, reduces the dirty data 
			amount by turning off dirty flags until the flushed amount reached 
			the amount passed in or there is no dirty data left in cache. 
			Similarly, periodical flushing is the function that simulates data flushing 
			during CPU time and cache read. However, the flushed data amount is 
			calculated with the input which is flushing time. In both flushing 
			functions, the last block being flushed is split if its data is not 
			entirely flushed.
